---
title: 'This page and the next page should be manually removed. Template used: https://osf.io/g7dbt.'
shorttitle: 'Subliminal Header'

csl:                "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass:      apa7
classoption:        man
fontsize:           12pt
linestretch:        1.5
floatsintext:       yes
figurelist:         no
tablelist:          no
footnotelist:       no
linenumbers:        no
mask:               no

bibliography: ['references.bib', 'package-references.bib']

output:
  papaja::apa6_pdf:
    extra_dependencies: ['flafter']   # Place tables and figures below where they are first mentioned in the text.
      
# Latex preamble specifying layout
header-includes:
  - \setcounter{tocdepth}{3}
  - \addtolength\oddsidemargin {0.5cm}
  - \addtolength\evensidemargin {-0.5cm}
  - \linespread{1.2} 
  - \usepackage{changepage} 
  - \usepackage{setspace} 
  - \shorttitle{}
  - \usepackage{fancyhdr} 
  - \fancyhf{}
  - \cfoot{\thepage}
  - \pagestyle{fancy}
  - \renewcommand{\headrulewidth}{0pt}
  - \pagestyle{plain}
  - \interfootnotelinepenalty=10000
  - \renewcommand{\topfraction}{.75}        # Reduce page margins
  - \renewcommand{\bottomfraction}{.4}      # Reduce page margins
  - \renewcommand{\textfraction}{.15}       # Reduce page margins
  - \renewcommand{\floatpagefraction}{.6}   # Reduce page margins
  - \setlength{\@fptop}{0pt}                # Vertically-align tables and figures to the top
  - \setcounter{topnumber}{3}               # Reduce page margins
  - \setcounter{bottomnumber}{2}            # Reduce page margins
  - \setcounter{totalnumber}{4}             # Reduce page margins
  - \usepackage{placeins}                   # Allow use of `\FloatBarrier` to position tables and figures
  - \usepackage{amsmath}                    # Maths formatting
  - \usepackage{upgreek}                    # Disable the italicisation of Greek letters
  - \usepackage{booktabs}                   # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{longtable}                  # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{array}                      # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{multirow}                   # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{wrapfig}                    # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{float}                      # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{colortbl}                   # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{pdflscape}                  # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{tabu}                       # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{threeparttable}             # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{threeparttablex}            # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage[normalem]{ulem}             # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{makecell}                   # Dependency for R package 'kableExtra' (table formatting)
  - \usepackage{xcolor}                     # Dependency for R package 'kableExtra' (table formatting)
  - \renewcommand\appendix{}                # Remove redundant 'Appendix' label
---


\clearpage\mbox{}\thispagestyle{empty}\clearpage

\setcounter{page}{1}

\thispagestyle{empty}
\begin{center}
\vspace*{20mm}
\textbf{\Large
Language and sensorimotor simulation in conceptual  \\ 
\bigskip
processing: Multilevel analysis and statistical power
}\\

\vspace*{26mm}

\textbf{\Large Pablo César de Juan Bernabéu }\\

\vspace*{30mm}

{\large \setstretch{1.7}
This thesis is submitted for the degree of  \\
Doctor of Philosophy in Psychology.  \\
\bigskip
\bigskip
Lancaster University  \\
Department of Psychology  \\
\bigskip
\bigskip
October 2022
}
\end{center}

\newpage


# Abstract

Research has suggested that conceptual processing depends on both language-based and sensorimotor information. In this thesis, I investigate the nature of these systems and their interplay at three levels of the experimental structure---namely, individuals, words and tasks. In Study 1, I contributed to a multi-lab replication of the object orientation effect, which has been used to test sensorimotor simulation. The effect did not appear across any of the 18 languages examined, and it was not influenced by individual differences in mental rotation. Next, in Study 2, we drew on three existing data sets that implemented semantic priming, semantic decision and lexical decision. We extended these data sets with measures of language-based and vision-based information, and analysed their interactions with participants' vocabulary size, gender and presentation speed. The analysis had a conservative structure of fixed and random effects. First, we found that language-based information was found to be more important than vision-based information. Second, in the semantic priming study---whose task required distinguishing between words and nonwords---, both language-based and vision-based information were more influential when words were presented faster. Third, a 'task-relevance advantage' was identified in higher-vocabulary participants. Specifically, in lexical decision, higher-vocabulary participants were more sensitive to language-based information than lower-vocabulary participants. In contrast, in semantic decision, higher-vocabulary participants were more sensitive to word concreteness. Fourth, we demonstrated the influence of the analytical method on the results. Last, we estimated the sample size required to investigate various effects. We found that 300 participants were sufficient to examine the effect of language-based information in words, whereas more than 1,000 participants were necessary for the effect of vision-based information and for the interactions of both former variables with vocabulary size, gender and presentation speed. This power analysis reveals the need to increase sample sizes for research on perceptual simulation and individual differences. 

\newpage


\begin{flushleft}
{\setstretch{1.0}
\tableofcontents
}
\end{flushleft}

\newpage 



# Acknowledgements

Thank you to my supervisors, Dr. Dermot Lynott and Prof. Louise Connell, for your invaluable advice and encouragement. This journey has been as interesting and academically enriching for me as I had hoped. I equally value the personal support from Dermot when it was needed. Thank you also to all my colleagues, including the members of the Embodied Cognition Lab, as well as all the faculty and the students I worked with as a graduate teaching assistant. I very much enjoyed working with you, and learned a lot in the process. Thank you very much to the Department of Psychology at Lancaster University for their fundamental support throughout my PhD. Thank you to all the staff who have guided and helped me along the way, at my department, at the Information Systems Services, and at the High-End Computing facility. Thank you to Gorilla Experiment Builder and to Prolific for a joint grant that will support my next study, and for their help with my questions. Thank you to the Software Sustainability Institute, the RepliCATS project and the Open Scholarship Community Galway for their indulgence and their awards, which helped support my PhD research, broadened my professional horizons, and allowed me to meet many interesting people. Thank you to the contributors who addressed my questions on StackExchange and other forums. Thank you to Dr. Margriet Groen and Prof. Max Louwerse for their attention as the examiners of my PhD. Last but not least, thank you to my family and my friends for all the talks talked and the walks walked.

\newpage


# Declaration

The work submitted in this thesis is my own and has not been submitted in substantially the same form towards the award of another degree or other qualifying work by myself or by any other person. All sources have been referenced. Correspondence can be addressed to pcbernabeu@gmail.com.

The materials needed to reproduce this thesis are available at https://osf.io/gt5uf. The creation of this document drew on the R packages 'rmarkdown' [@R-rmarkdown_b] and 'papaja' [@R-papaja], and the LaTeX package 'apa7' [@weiss-apa7-2022]. Whereas the aforementioned materials will not be further modified, readers can also consult the developing materials for Study 1 at https://osf.io/e428p, and those for Study 2 at https://osf.io/ueryq. 

My role in Study 1 [@chenInvestigatingObjectOrientation2018] has consisted of theoretical, methodological and stylistic suggestions during the design of the study, the creation of a video demonstrating our procedure (https://osf.io/h36wr), the collection of data from 50 participants (https://osf.io/waf48), and the provision of feedback about the analysis of the data and the reporting of the results. My primary supervisor, Dr. Dermot Lynott, advised me throughout this project, and he contributed to the study himself. Next, I look forward to working on the last revisions of the manuscript. The current manuscript is not included in this thesis due to its developing state. However, it has been shared with the examiners of my PhD (Dr. Margriet Groen and Prof. Max Louwerse), and the status of the project is available at https://psysciacc.org/002-object-orientation. The Stage I Registered Report was accepted in the journal Psychonomic Bulletin & Review, where the final version is expected to be published over the following months. 

My role in Study 2 spanned the entire study, comprising the design of the study, the collation and preprocessing of the data, the statistical analysis, the documentation (https://osf.io/ueryq/wiki) and the reporting. Furthermore, Dr. Dermot Lynott contributed to the design of the study and provided theoretical, methodological and stylistic advice throughout the project. My secondary supervisor, Prof. Louise Connell, contributed to the design of the study and provided occasional advice afterwards. 

\newpage



```{r setup, include = FALSE}

# General knitr options
knitr::opts_chunk$set(cache = FALSE, message = FALSE, warning = FALSE, 
                      error = FALSE, echo = FALSE, 
                      knitr.duplicate.label = 'allow', 
                      fig.align = 'center', dev = 'CairoPDF', 
                      knitr.graphics.auto_pdf = TRUE, dpi = 72, 
                      out.width = '100%')

library(papaja)       # APA-formatted manuscript
library(knitr)        # Document rendering
options(kableExtra.latex.load_packages = FALSE)  # instead, LaTeX packages loaded in header/preamble above
library(kableExtra)   # Tables
library(dplyr)        # Data wrangling
library(formattable)  # Format numbers
library(kableExtra)   # Table formatting (e.g., `pack_rows()`)
library(stringr)      # Text processing
library(ggplot2)      # Plots
library(GGally)       # Correlation plots
library(sjPlot)       # Model plots
library(RColorBrewer) # Colours in plots
library(patchwork)    # Combination of plots
library(Cairo)        # Allows use of special characters such as dashes in plots
library(magick)       # Image rendering
library(tikzDevice)   # Image rendering

# Move working directory to the project root
knitr::opts_knit$set(root.dir = '../')

```


```{r load-functions-data-models, include = FALSE}

# Read in all custom functions
setwd('R_functions')
sapply(list.files(), source, echo = FALSE)
setwd('../')

# Load main data sets and models. These objects are loaded directly, rather than 
# being run on the go, to keep the knitting of the manuscript reasonably fast. 
# Crucially, however, all the objects can be reproduced from the appropriate R 
# scripts in the current project. For further details, see 'README.pdf' in 
# 'manuscript' directory. 

# Study 2.2.1: Semantic priming

# Code for data set below in 'semanticpriming/data' folder
semanticpriming = read.csv('semanticpriming/data/final_dataset/semanticpriming.csv')

# Code for models below in 'semanticpriming/frequentist_analysis' folder
semanticpriming_lmerTest =   # Primary model object
  readRDS('semanticpriming/frequentist_analysis/results/semanticpriming_lmerTest.rds')
KR_summary_semanticpriming_lmerTest =   # Model with Kenward-Roger p values
  readRDS('semanticpriming/frequentist_analysis/results/KR_summary_semanticpriming_lmerTest.rds')
confint_semanticpriming_lmerTest =   # Confidence intervals
  readRDS('semanticpriming/frequentist_analysis/results/confint_semanticpriming_lmerTest.rds')


# Subset of the semantic priming study that included vision-based similarity.
# Code for data set below in 'semanticpriming/data' folder
semanticpriming_with_visualsimilarity = 
  read.csv('semanticpriming/data/subset_with_visualsimilarity/semanticpriming_with_visualsimilarity.csv')

# Code for models below in 'semanticpriming/semanticpriming_with_visualsimilarity' folder
semanticpriming_with_visualsimilarity_lmerTest =   # Primary model object
  readRDS('semanticpriming/analysis_with_visualsimilarity/results/semanticpriming_with_visualsimilarity_lmerTest.rds')
KR_summary_semanticpriming_with_visualsimilarity_lmerTest =   # Model with Kenward-Roger p values
  readRDS('semanticpriming/analysis_with_visualsimilarity/results/KR_summary_semanticpriming_with_visualsimilarity_lmerTest.rds')
confint_semanticpriming_with_visualsimilarity_lmerTest =   # Confidence intervals
  readRDS('semanticpriming/analysis_with_visualsimilarity/results/confint_semanticpriming_with_visualsimilarity_lmerTest.rds')

# Code for models below in 'semanticpriming/bayesian_analysis' folder
semanticpriming_summary_informativepriors_exgaussian = 
  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_informativepriors_exgaussian.rds')
semanticpriming_summary_weaklyinformativepriors_exgaussian = 
  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_weaklyinformativepriors_exgaussian.rds')
semanticpriming_summary_diffusepriors_exgaussian = 
  readRDS('semanticpriming/bayesian_analysis/results/semanticpriming_summary_diffusepriors_exgaussian.rds')


# Study 2.2: Semantic decision
# Code for data set below in 'semanticdecision/data' folder
semanticdecision = read.csv('semanticdecision/data/final_dataset/semanticdecision.csv')

# Code for models below in 'semanticdecision/frequentist_analysis' folder
semanticdecision_lmerTest =   # Primary model object
  readRDS('semanticdecision/frequentist_analysis/results/semanticdecision_lmerTest.rds')
KR_summary_semanticdecision_lmerTest =   # Model with Kenward-Roger p values
  readRDS('semanticdecision/frequentist_analysis/results/KR_summary_semanticdecision_lmerTest.rds')
confint_semanticdecision_lmerTest =   # Confidence intervals
  readRDS('semanticdecision/frequentist_analysis/results/confint_semanticdecision_lmerTest.rds')

# Code for models below in 'semanticdecision/bayesian_analysis' folder
semanticdecision_summary_informativepriors_exgaussian = 
  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_informativepriors_exgaussian.rds')
semanticdecision_summary_weaklyinformativepriors_exgaussian = 
  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_weaklyinformativepriors_exgaussian.rds')
semanticdecision_summary_diffusepriors_exgaussian = 
  readRDS('semanticdecision/bayesian_analysis/results/semanticdecision_summary_diffusepriors_exgaussian.rds')


# Study 2.3: Lexical decision
# Code for data set below in 'lexicaldecision/data' folder
lexicaldecision = read.csv('lexicaldecision/data/final_dataset/lexicaldecision.csv')

# Code for models below in 'lexicaldecision/frequentist_analysis' folder
lexicaldecision_lmerTest =   # Primary model object
  readRDS('lexicaldecision/frequentist_analysis/results/lexicaldecision_lmerTest.rds')
KR_summary_lexicaldecision_lmerTest =   # Model with Kenward-Roger p values
  readRDS('lexicaldecision/frequentist_analysis/results/KR_summary_lexicaldecision_lmerTest.rds')
confint_lexicaldecision_lmerTest =   # Confidence intervals
  readRDS('lexicaldecision/frequentist_analysis/results/confint_lexicaldecision_lmerTest.rds')

# Code for models below in 'lexicaldecision/bayesian_analysis' folder
lexicaldecision_summary_informativepriors_exgaussian = 
  readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_informativepriors_exgaussian.rds')
lexicaldecision_summary_weaklyinformativepriors_exgaussian = 
  readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_weaklyinformativepriors_exgaussian.rds')
lexicaldecision_summary_diffusepriors_exgaussian = 
  readRDS('lexicaldecision/bayesian_analysis/results/lexicaldecision_summary_diffusepriors_exgaussian.rds')

```



```{r, child = 'thesis/Chapter-1-Introduction.Rmd'}
```

\clearpage

```{r, child = 'thesis/Chapter-2-Study-1.Rmd'}
```

\clearpage

```{r, child = 'thesis/Chapter-3-Study-2.Rmd'}
```

\clearpage

```{r, child = 'thesis/Chapter-4-General-discussion.Rmd'}
```

\clearpage



# (APPENDIX) Appendix {-}

<!-- Every appendix must be referenced below (see https://github.com/crsh/papaja/issues/496#issuecomment-996084228) -->

<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{A\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}} \setcounter{table}{0}

```{r, child = 'thesis/appendix-A-lexical-covariates.Rmd'}
```

\clearpage


<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{B\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}} \setcounter{table}{0}

```{r, child = 'thesis/appendix-B-frequentist-analysis-diagnostics.Rmd'}
```

\clearpage


<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{C\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{C\arabic{table}} \setcounter{table}{0}

```{r, child = 'thesis/appendix-C-Bayesian-analysis-diagnostics.Rmd'}
```

\clearpage


<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{D\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{D\arabic{table}} \setcounter{table}{0}

```{r, child = 'thesis/appendix-D-interaction-plots.Rmd'}
```

\clearpage


<!-- Following APA format, precede figure and table numbers with the title letter of this appendix -->
\renewcommand{\thefigure}{E\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{E\arabic{table}} \setcounter{table}{0}

```{r, child = 'thesis/appendix-E-Bayesian-analysis-results.Rmd'}
```

\clearpage



# References

::: {#refs}
:::

